### 2021-11-05 NSF2021/Description/specificaim3.tex
yny

\subsection{Specific Aim 3: Dynamics of self-assembly by HAP under an external flow/field}
\label{subsec:specific_aim_3}

\subsubsection{Vesicles in background flows}
Numerically solving the Stokes and screened Laplace system~\eqref{SL}
and~\eqref{eq:stokes} is nontrivial, and we will develop efficient,
robust, high-order-in-time and -space algorithms suited to the problem.
There are a few challenges. {\bf (i)} The equations express a two-way
coupling since the flow changes the position of the suspended particles,
and in return, the geometry-dependent hydrophobic stresses impart a
force on the flow. {\bf (ii)} The inputs to the Stokes equations are
particle configurations, forces, and torques. The outputs are the rigid
body translation and angular velocities used to update the particle
positions (see Figure~\ref{fig:flow_map}). Although the underlying
equations are linear, the overall problem is highly nonlinear because
the domain is constantly changing. {\bf (iii)} Self-assembly causes the
particles to come into close contact. As a result, an exceptional
spatial accuracy is required to resolve the fields between adjacent
particles. Furthermore, physically relevant elastic properties of
bilayers become apparent at large length scales and for large
particle-numbers, which increases the computational complexity of our
simulations.

We include a background flow by replacing the third equation in
\eqref{eq:stokes} with the condition $\mathbf{u}(\mathbf{x})
\to \mathbf{u}_{\infty}(\mathbf{x})$ as $|\mathbf{x}| \to
\infty$. To incorporate the far-field flow, we use the representation 
\begin{align}
\label{PowerMiranda}
  {\bf u} = {\bf u}_{\infty} + \mathcal{K}\boldsymbol{\eta} + 
    \sum_{i=1}^N \left(S(\cdot, {\bf a}_i) {\bf F}_i + 
                 R(\cdot, {\bf a}_i) {\bf G}_i\right),
\end{align}
where $S$ and $R$ are stokeslets and rotlets supported at the respective
particle centers~\cite{leal_2007} and $\mathcal{K}\boldsymbol{\eta}$ is a layer
potential for the unknown density function $\boldsymbol{\eta}$. With the
exception of the rigid body conditions, the
representation~\eqref{PowerMiranda} automatically satisfies all the
hydrodynamic equations including the far-field condition. The rigid
body conditions follow by requiring the viscous stresses to vanish across
the particle boundaries.
%
We will compare the behavior of our particle-based vesicles in Stokes
flow to well-established models that enforce area incompressibility and
volume conservation in vesicle membrane
dynamics~\cite{torres-sanchez_millan_arroyo_2019,mahapatra_saintillan_rangamani_2020, Steigmann99, C6SM02452A}.
\S \ref{sec:preliminary_work} contains our preliminary results.
%
%Our
%preliminary results show that the particle-based bilayers have the same
%large area modulus as real lipid bilayer membranes, so we expect
%realistic results from our flow simulations. Under moderate shear rates,
%the vesicle elongates and takes on the tank-treading elliptical shape.
%We can directly check for area compressibility and volume conservation
%properties from particle simulations by tracking the change in area
%density of the midplane as a function of shear flow rate, along with
%evaluating the tangential divergence of the velocity.
%
%Bilayer membranes have a small permeability to
%water~\cite{323e9a2f0c58487ea82518d7a1f96485}, and modelers often assume
%a vesicle membrane that conserves volume. In our particle-based
%approach, water motion across the bilayer is limited by the size of the
%gaps between the particles, which is an artifact of coarse-graining.
%Making these gaps smaller comes at the expense of numerical accuracy,
%and we will assess if there is a reasonable trade-off between
%approximate volume conservation and simulation complexity. 
%
%Finally, the particle-based vesicle bilayers have two distinct leaflets
%consisting of the particles in contact with the vesicle interior, and
%those in contact with the surrounding fluid. Since there is a nonzero
%separation between these layers, an important effect we observe is that
%the leaflets slide against one another under shear flow. This implies
%that part of the viscous dissipation in the aqueous phase is enhanced by
%intermonolayer friction~\cite{SHKULIPA2005823, ShkulipaThesis}.
%Intermonolayer slip enters zero-thickness membrane models as a velocity
%jump boundary condition and leads to multiple solution
%states~\cite{schwalbe_vlahovska_miksis_2010}. In the present proposal,
%intermonolayer slip is an artifact of monolayer independence and we can
%control for slip as a function of shear rate, vesicle diameter, and
%particle geometry.

>>>>

\subsection{Specific Aim 3: Self-assembly of Janus particles in ionic solutions}
\label{subsec:specific_aim_3}

\subsubsection{Dynamics of a single Janus particle in ionic solutions}
In experiments, Janus particles are often immersed in a solution of ions \cite{ChenWhitmer2011_Sci} or surfactants \cite{}.
In electrolytic solutions the interaction between salt and Janus particle gives 
rise to a slip velocity (on the particle surface) that depends on the ion distribution and the zeta potential \cite{BayatiJCP2016} 
(the potential difference between the Janus particle surface and the surrounding conducting fluid).
The short-range interactions between Janus particles depend on the salt concentration:
At very low salt concentrations, Janus particles repel one another electrostatically, whereas at high salt concentration, van der Waals
forces cause Janus particles to aggregate irreversibly \cite{Goodwin2019}. At intermediate concentrations of monovalent salt, Janus particles are found to self assemble in the form of a small number of elemental units of building blocks \cite{Chen2011_Science}. 
%
\begin{wrapfigure}[11]{l}{0.47\textwidth}
\centerline{\includegraphics[width=0.46\textwidth]{Figures/fig2A_Chen2011_Science}}
  \vspace{-5pt}
\caption{\label{fig:helices_of_JPs} \footnotesize Formation of helices of Janus particles as salt concentration increases \cite{Chen2011_Science}.}
\end{wrapfigure}
%
Figure~\ref{fig:helices_of_JPs} shows that Janus particles can self-assemble into a helix at high concentration of monovalent salt (NaCl) when the density of Janus particles is low to moderate. At high density, JPs are found to form wormlike structures

The Stokes equations in~\eqref{eq:stokes} are modified to incorporate the transport of ions as
\begin{equation}
\label{eq:stokes}
\begin{aligned}
  &-\mu \Delta \mathbf{u} + \nabla p = \Delta\psi\cdot\nabla\psi, \quad \mathbf{x} \in \Omega, \qquad
  \nabla \cdot \mathbf{u} = 0,  \quad \mathbf{x} \in \Omega,\\
  &\delta^2\Delta\psi = -\frac{1}{2}\left(n_+-n_-\right),\qquad
  \frac{\partial n_{\pm}}{\partial t} + \nabla\cdot{\bf j}_{\pm} = 0,\\
  &{\bf j}_{\pm} = -\nabla n_{\pm \mp n_{\pm} \nabla\psi + Pe n_{\pm}\mathbf{u}.
\end{aligned}
\end{equation}
The screen length $\rho$ is now a function of the ion concentrations: $\rho = \rho(n_+,n_-)$.
